ActiveCA: Time Use Data from the General Social Survey of Canada to Study Active Travel

### 2024-11-17 data-raw/02-calculating-impedances.Rmd
Improved the documentation and fixed an issue with the Cycle 2 (1986) episode weights, which did not correctly use the number of decimals indicated in the user's guide

```{r}
load(file = paste0(here(), "/data/walking_1986.Rda"))
```

@@

```{r}
for(destino in unique(tld_empirical$destination)){
  assign(paste0("f_1986_Walking_dest", destino), 
         test_distributions_weighted(
           x = tld_empirical[tld_empirical$destination == destino, ]$DURATION,
           weights = tld_empirical[tld_empirical$destination == destino, ]$WGHT_EPI))
}
```

@@

```{r}
load(file = paste0(here(), "/data/gss_episodes.Rda"))
```

@@

```{r}
gss_impedances <- gss_episodes[,c("PUMFID","DURATION","LOCATION",
                  "origin","destination","Province","Pop_centre","orig_label",
                  "dest_label","YEAR","MODE","f_name",
                  "f","est_1","est_2","loglik","aic","bic","count")]
```

>>>>

```{r}
load(file = paste0(here(), "/data/walking_1986.rda"))
```

@@

```{r}
for(destino in unique(tld_empirical$destination)){
  assign(paste0("f_1986_Walking_dest", destino), 
         test_distributions_weighted(
           x = tld_empirical[tld_empirical$destination == destino, ]$DURATION,
           weights = round(tld_empirical[tld_empirical$destination == destino, ]$WGHT_EPI)))
}
```

@@

```{r}
load(file = paste0(here(), "/data/gss_episodes.rda"))
```

@@

```{r}
gss_impedances <- gss_episodes[,c("PUMFID","DURATION",
                                  "origin","destination","Province","Pop_centre","orig_label",
                                  "dest_label","YEAR","MODE","f_name",
                                  "f","est_1","est_2","loglik","aic","bic","count")]
```

### 2024-11-17 paper/Manuscript-Data-Package.Rmd
Improved the documentation and fixed an issue with the Cycle 2 (1986) episode weights, which did not correctly use the number of decimals indicated in the user's guide

---
title: "ActiveCA: Time Use Data from the General Social Survey of Canada to Study Active Travel"
author:
  - name: "Anon1"
    email: "Anon1@anon.org"
    affiliation: CODE
    footnote: 1
  - name: "Anon2"
    email: "Anon2@anon.org"
    affiliation: CODE
  - name: "Anon3"
    email: "Anon3@anon.org"
    affiliation: CODE
address:
  - code: CODE
    address: "Some school"
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: 
  "This paper describes the open data product {ActiveCA}. {ActiveCA} is an `R` data package that contains analysis-ready data from the General Social Survey cicles regarding active travel in Canada. The package provides data set detailing active trip origins, destinations, and duration, covering a wide variety of locations, such as home, work or school, libraries, museums, restaurants, bars, sports centers, health clinics, place of worship, and others. The package also details the respondent's region characteristics, specifying wheter they live in a metropolitan area and their province of residency. {ActiveCA} also provides pre-estimated impedance functions for active travel for Canadian Metropolitan Area and Census Agglomerations, which can be used in accessibility analysis to calculate the cost of travel between different locations. The package will continue to expand with contributions from the authors and the broader community through requests in the future. {ActiveCA} is freely accessible for exploration and download from the associated Github repository, where the documentation and code involved in creating and manipulating data are detailed."

>>>>

---
title: "ActiveCA: Time Use Data from the General Social Survey of Canada to Study Active Travel"
author:
  - name: "Anon1"
    email: "Anon1@anon.org"
    affiliation: CODE
    footnote: 1
  - name: "Anon2"
    email: "Anon2@anon.org"
    affiliation: CODE
  - name: "Anon3"
    email: "Anon3@anon.org"
    affiliation: CODE
address:
  - code: CODE
    address: "Some school"
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: 
  "This paper describes the open data product, {ActiveCA}, with Canadian time use data about active travel. {ActiveCA} is an `R` data package that contains analysis-ready data from cycles  General Social Survey cicles regarding active travel in Canada. The package provides data set detailing active trip origins, destinations, and duration, covering a wide variety of locations, such as home, work or school, libraries, museums, restaurants, bars, sports centers, health clinics, place of worship, and others. The package also details the respondent's region characteristics, specifying wheter they live in a metropolitan area and their province of residency. {ActiveCA} also provides pre-estimated impedance functions for active travel for Canadian Metropolitan Area and Census Agglomerations, which can be used in accessibility analysis to calculate the cost of travel between different locations. The package will continue to expand with contributions from the authors and the broader community through requests in the future. {ActiveCA} is freely accessible for exploration and download from the associated Github repository, where the documentation and code involved in creating and manipulating data are detailed."
